### 2012-10-13 notes.tex
Fixed and added some update equations in the notes.

{\bf Update Equations}
Isolating the terms of \eqref{eqn:composite} that involve $u_0$ gives
\begin{equation}
\mathcal{L}_{[u_0]} = K\sum_{j=1}^J\left(-\frac{1}{2\sigma_0^2}(\gamma_{1j}-u_0)^2\right)
\end{equation}

Taking the derivative with respect to $u_0$ gives

Solving for $u_0$ gives
\begin{equation}
u_0 \leftarrow \frac{1}{J}\sum_{j=1}^J \gamma_{1j} 
\end{equation}

@@

Isolating terms that involve $\alpha_{kj}$ gives
\begin{multline}
\mathcal{L}_{[\alpha_{kj}]} = (u_0M_0 -1)(\psi(\alpha_{kj}) - \psi(\alpha_{kj}-\beta_{kj}) -((1-u_0)M_0-1)\psi(\alpha_{kj}+\beta_{kj})\\
 +r_{kj}*\psi(\alpha_{kj})-n_{kj}\psi(\alpha_{kj}+\beta_{kj}) -\log \Gamma (\alpha+\beta) + \log \Gamma(\alpha) -(\alpha-1)\psi(\alpha)+(\alpha+\beta-2)\psi(\alpha+\beta)
\end{multline}

Setting the derivative equal to zero and solving for $\alpha_{kj}$ gives
\begin{equation}
\alpha_{kj} \leftarrow \psi_1(\alpha_{kj})(u_0M_0+r-\alpha_{kj}) - \psi_1(\alpha_{kj}+\beta_{kj})(M_0+n-(\alpha_{kj}+\beta_{kj}))
\end{equation}

@@

@@

>>>>

{\bf Update Equation for $u_0$ }

Isolating the terms of \eqref{eqn:composite} that involve $u_0$ gives
\begin{equation}
\mathcal{L}_{[u_0]} = K\sum_{j=1}^J\left(-\frac{1}{2\sigma_0^2}(\gamma_{1j}-u_0)^2\right)
\end{equation}

Taking the derivative and solving for $u_0$ gives
\begin{equation}
u_0 \leftarrow \frac{1}{J}\sum_{j=1}^J \gamma_{1j} 
\end{equation}

{\bf Update Equation for $\sigma_0^2$ }

@@

{\bf Update Equation for $\alpha_{kj}$ and $\beta_{kj}$ }

Isolating terms that involve $\alpha_{kj}$ gives
\begin{multline}
\mathcal{L}_{[\alpha_{kj}]} = (u_0M_0 -1)(\psi(\alpha_{kj}) - \psi(\alpha_{kj}+\beta_{kj})) -((1-u_0)M_0-1)\psi(\alpha_{kj}+\beta_{kj}) \\
+ r_{kj}\psi(\alpha_{kj})-n_{kj}\psi(\alpha_{kj}+\beta_{kj}) \\
 - \log \Gamma (\alpha_{kj}+\beta_{kj}) + \log \Gamma(\alpha_{kj}) -(\alpha_{kj}-1)\psi(\alpha_{kj})+(\alpha_{kj}+\beta_{kj}-2)\psi(\alpha_{kj}+\beta_{kj})
\end{multline}

Setting the derivative equal to zero and solving for $\alpha_{kj}$ gives
\begin{equation}
 \frac{\partial \mathcal{L}}{\partial \alpha_{kj}} = \psi_1(\alpha_{kj})(u_0M_0+r-\alpha_{kj}) - \psi_1(\alpha_{kj}+\beta_{kj})(M_0+n-(\alpha_{kj}+\beta_{kj}))
\end{equation}

@@

{\bf Update Equation for $M_0$ }

@@

Taking the derivative with respect to $\gamma_{2j}$ gives
\begin{equation}\label{eqn:gam2_deriv}
\frac{\partial \mathcal{L}}{\partial \gamma_{2j}} = -\frac{K}{2\sigma_0^2} -\frac{\partial}{\partial \gamma_{2j}}\E_q\log\Gamma(\mu_jM_0) -\frac{\partial}{\partial \gamma_{2j}}\E_q\log\Gamma((1-\mu_j)M_0) +\frac{1}{2\gamma_{2j}}
\end{equation}

The two partials are very similar, so we show only the derivation of the first and apply the solution to the second replacing $\mu_j$ with $(1-\mu_j)$ in the gamma function.
\begin{align}\label{eqn:gam2_int1}
\frac{\partial}{\partial \gamma_{2j}}\E_q\log\Gamma(\mu_jM_0) &= \frac{\partial}{\partial \gamma_{2j}} \int_0^1 (2\pi\gamma_{2j})^{-1/2}\exp\left(-\frac{1}{2\gamma_{j2}}(\mu_j-\gamma_{1j})^2\right) \log\Gamma(\mu_jM_0)d\mu_j \\
& = \frac{1}{2\gamma_{2j}}\left(\frac{1}{\gamma_{2j}} \E_q \left[ (\mu_j-\gamma_{1j})^2 \log\Gamma(\mu_jM_0) \right] - \E_q \left[ \log\Gamma(\mu_jM_0) \right] \right)
\end{align}

Replacing \eqref{eqn:gam2_int1} in \eqref{eqn:gam2_deriv} gives
\begin{multline}
\frac{\partial \mathcal{L}}{\partial \gamma_{2j}} = -\frac{K}{2\sigma_0^2} 
- \frac{1}{2\gamma_{2j}}\left(\frac{1}{\gamma_{2j}} \E_q \left[ (\mu_j-\gamma_{1j})^2 \log\Gamma(\mu_jM_0) \right] - \E_q \left[ \log\Gamma(\mu_jM_0) \right] \right) \\
- \frac{1}{2\gamma_{2j}}\left(\frac{1}{\gamma_{2j}} \E_q \left[ (\mu_j-\gamma_{1j})^2 \log\Gamma((1-\mu_j)M_0) \right] - \E_q \left[ \log\Gamma((1-\mu_j)M_0) \right] \right) +\frac{1}{2\gamma_{2j}}
\end{multline}
Solving for the root gives the maximizing value of $\gamma_{2j}$ and the update.
